Mental Health Plays Significant Role in Physical Wellnesss in 1972 to 2022 US General Social Surveys

### 2024-04-15 paper/paper.qmd
update paper and preamble of the model.R script

---
title: "Mental Health Plays Significant Role in Physical Wellness"
subtitle: "Intersectionality and Mental Illness Being Overlooked in the Medical Field"
author: 
  - Mingjia Chen
thanks: "Code and data are available at: https://github.com/MjChen120/Mental_to_Physical_Health.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Mental health is one essential aspect of the general health of an individual and yet it is often overlooked in the past centuries. Mental illnesses are not only “silent diseases” of one’s mind, but could as well impact patients’ physical well-being in general [@Ohrnberger_Fichera_Sutton]. As browsing through relevant journal articles, a question arises: could mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month?

U.S. General Social Survey (GSS) data is used for this paper to examine whether the demographic and mental health-related factors as indicators of physical health conditions. The estimand is the difference in whether an individual could experience more occasions of feeling physically unwell if they have mental health unwellness versus not. This is considered in terms of those who were diagnosed as having depression by a doctor.

@@

some words

@@

```

@@

@@

>>>>

---
title: "Mental Health Plays Significant Role in Physical Wellnesss in 1972 to 2022 US General Social Surveys"
subtitle: "Racial and Gender Unequity and Mental Illness Being Overlooked in the Medical Field"
author: 
  - Mingjia Chen
thanks: "Code and data are available at: https://github.com/MjChen120/Mental_to_Physical_Health.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Mental health is one essential aspect of the general health of an individual and yet it is often overlooked. Mental illnesses are not only “silent diseases” of one’s mind, but could as well impact patients’ physical well-being in general [@Ohrnberger_Fichera_Sutton]. This paper examines whether mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month?

U.S. General Social Survey (GSS) data from 1972 to 2022 is used for this paper to examine whether the demographic and mental health-related factors as indicators of physical health conditions. The estimand is the difference in whether an individual could experience more occasions of feeling physically unwell if they have mental health unwellness versus not. This is considered in terms of those who were diagnosed as having depression by a doctor.

@@

will be written

@@

@@

\break

@@

will be written
